\documentclass[11pt]{article}
\usepackage[letterpaper,margin=0.2in]{geometry}
\linespread{0.5}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{xcolor}
\usepackage{url}
\pagestyle{fancy}
\cfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\setlength\headsep{0.333in}

\begin{document}
\begin{flushleft}

    \makebox[\textwidth]{\LARGE \textbf{\textcolor{teal}{Tyler Kaminski}}}\\

\setlength{\parindent}{0.5in}

\begin{multicols}{2}
    \textbf{tyjoka@protonmail.com} \textemdash{} (973) 529-2539
    \textbf{tkamins1@stevens.edu}
\end{multicols}

\begin{itemize}
    \item[] \Large \textcolor{blue}{\textbf{Education}} \normalsize
        \begin{itemize}
            \item Stevens Institute of Technology, \textit{Hoboken, NJ}  \hfill{\textbf{(Aug. 2019 - Present)}}
                \begin{itemize}
                    \item GPA - 3.773
                    \item Bachelors of Science in Computer Science \hfill{Expected Graduation \textbf{May 2022}}
					\item \textcolor{violet}{Honors}: FIRST Robotics Scholarship, Edwin A. Stevens Scholarship, Presidential Scholarship, Dean’s List (19F - Present)
                    \item \textcolor{blue}{Coursework}: Algorithms (\textbf{C++}), Computer Organization and Programming (\textbf{ARMv8 + C}), Automata and Computation, Systems Programming (\textbf{Bash + C}), Introduction to Text Mining and Statistical Natural Language Processing (\textbf{Python - NLTK + Scikit-learn}), Computer Vision (\textbf{Python - OpenCV}), Concurrent Programming (\textbf{Erlang}), Systems Administration (\textbf{POSIX shell}), Systems Security (\textbf{Python, C, x86}), Operating Systems (\textbf{C}), Quantitative Biology (\textbf{Python - Scikit-learn}), Agile Methods for Software Development.
                \end{itemize}
        \end{itemize}
	\item[] \Large \textcolor{blue}{\textbf{Skills}} (\url{linkedin.com/in/tyka}) \normalsize
        \begin{itemize}
            \item Comfortable with C and C++, Bash/POSIX shell, Linux and UNIX System Administration, Python, ARMv8, AWK/sed, Git, Vim, LaTeX, and HTML/CSS.
            \item Proficient with Erlang, OCaml, sqlite, mariaDB, postgreSQL, GTK, R, LISP, and JS.
        \end{itemize}
        \item[] \Large \textcolor{blue}{\textbf{Work Experience}} \normalsize
            \begin{itemize}
                \item \textbf{Systems Programming Course Assistant}, Stevens Institute of Technology \hfill{\textbf{(Jan. 2022 - Present)}}
                    \begin{itemize}
                        \item Taught principles of low-level Linux systems programming in C and held office hours for student questions. Helped students in understanding UNIX file pointers, robust input validation, and memory allocation.
                    \end{itemize}
                \item \textbf{Computer Organization Course Assistant}, Stevens Institute of Technology \hfill{\textbf{(Aug. - Dec. 2021)}}
                    \begin{itemize}
                        \item Taught principles of computer architecture and organization to students through hands-on labs focused on writing programs in ARMv8 and during office hours. Helped students in understanding assembly programming, stack management, and the basics of translation from highler-level languages to assembly.
                    \end{itemize}
                \item \textbf{Information Technology Intern}, Ricoh, \textit{Brooklyn, NY} \hfill{\textbf{(Jun. - Aug. 2021)}}
                    \begin{itemize}
                        \item Managed technology infrastructure of charter schools throughout Brooklyn.
						\item Oversaw Microsoft Active Directory user creation, teacher profile setup, laptop hardware and software troubleshooting and replacement.
                    \end{itemize}
            \end{itemize}
    \item[] \Large \textcolor{blue}{\textbf{Projects}} (\url{github.com/durcor}) \normalsize
        \begin{itemize}
            \item \textbf{blocks} \textit{POSIX shell, AWK} \hfill{\url{https://github.com/durcor/blocks}}
                \begin{itemize}
                    \item Using interfaces such as Linux's sysfs and curl to collect and process text for display in a status bar.
                \end{itemize}
            \item \textbf{ShadowRePlay} \textit{POSIX shell} \hfill{\url{https://github.com/MAPReiff/ShadowRePlay-Linux}}
                \begin{itemize}
					\item Unofficial port of NVIDIA's ShadowPlay functionality to Linux using ffmpeg, supporting GPU encoders (NVENC, AMF, QuickSync) and CPU encoding (libx264).
                \end{itemize}
            \item \textbf{oc} \textit{POSIX shell} \hfill{\url{https://github.com/durcor/oc}}
                \begin{itemize}
                    \item Utility for easily and automatically overclocking AMD GPUs on Linux.
                \end{itemize}
            \item \textbf{Linux System Automation} \textit{POSIX shell, vimscript} \hfill{\url{https://github.com/durcor/friedrice}}
                \begin{itemize}
                    \item Collection of shell scripts for automating Linux system administration, such as configuration file management and system administration.
                \end{itemize}
        \end{itemize}
    \item[] \Large \textcolor{blue}{\textbf{Leadership Experience}} \normalsize
        \begin{itemize}
            \item \textbf{Stevens Linux Users Group}, \textit{Hoboken, NJ} \hfill{\textbf{(Feb. 2020 - Present)}}
                \begin{itemize}
                    \item Founder and President
                    \item Organized logistics of organization creation, from communicating with student government and faculty to creating a budget and events.
                \end{itemize}
            \item \textbf{Hackettstown High School FIRST Robotics}, \textit{Hackettstown, NJ} \hfill{\textbf{(Sept. 2016 - Present)}}
                \begin{itemize}
                    \item Mentor for educating new team members with software and logistical team operations.
                    \item Quartermaster for inventorying and organizing team supplies.
                    \item Lead Graphics Designer - Designed graphics for team's shirts, spirit wear, and website/documents.
                    \item Head Field Scout - Provided scouting knowledge to the team with the data of other team's robots.
                \end{itemize}
            \item \textbf{Hackettstown High School Political Club}, \textit{Hackettstown, NJ} \hfill{\textbf{(Sept. 2015 - Jun. 2019)}}
                    \begin{itemize}
                        \item President - Directed club discussion, assisted club operation, and picked topics to discuss.
                    \end{itemize}
                \item \textbf{American Legion Jersey Boys State}, \textit{Lawrenceville, NJ} \hfill{\textbf{(Jun. 2018)}}
                    \begin{itemize}
                        \item Elected as a City Councilman - Completed city manual and solved issues through enacting ordinances.
                    \end{itemize}
            \end{itemize}
\end{itemize}

\end{flushleft}
\end{document}
